\input{chapter/Classes/Core/MORR/Data/Transcoding/Metadata/MetadataTranscoding}
\input{chapter/Classes/Core/MORR/Data/Transcoding/Video/VideoTranscoding}
\input{chapter/Classes/Core/MORR/Data/Transcoding/WinAPI/WinAPI_Transcoding}

\begin{interface}{IEncoder}
    \clsdcl{public interface IEncoder}

    \clsdsp{Encodes the provided samples into a file at a path.}

    \begin{attributes}
        \attribute{event VideoSampleRequestedEventHandler VideoSampleRequested}{Event raised when the next VideoSample may be added for encoding.}
        \attribute{event MetadataSampleRequestedEventHandler MetadataSampleRequested}{Event raised when the next MetadataSample may be added for encoding.}
    \end{attributes}

    \begin{methods}
        \begin{method}{void EncodeTo(string path)}{Encodes all provided sample to a file at the specified location.}
            \begin{parameters}
                \para{string path}{The path to encode to.}
            \end{parameters}
            \begin{exceptions}
                \excp{EncodingException}{Exception thrown if the encoding fails. This may be a MetadataEncodingException or a VideoEncodingException.}
            \end{exceptions}
        \end{method}
    \end{methods}
\end{interface}

\begin{interface}{IDecoder}
    \clsdcl{public interface IDecoder}

    \clsdsp{Decodes samples stored in a file at a path and provides the decoded samples.}

    \begin{attributes}
        \attribute{event VideoSampleDecodedEventHandler VideoSampleDecoded}{Event raised when a VideoSample gets decoded.}
        \attribute{event MetadataSampleDecodedEventHandler MetadataSampleDecoded}{Event raised when a MetadataSample gets decoded.}
    \end{attributes}

    \begin{methods}
        \begin{method}{void DecodeFrom(string path)}{Decodes samples contained in a file at a specified location.}
            \begin{parameters}
                \para{string path}{The path to decode from.}
            \end{parameters}
            \begin{exceptions}
                \excp{DecodingException}{Exception thrown if decoding fails. This may be a MetadataDecodingException or a VideoDecodingException.}
            \end{exceptions}
        \end{method}
    \end{methods}
\end{interface}

\begin{class}{EncodingException}
    \clsdcl{public class EncodingException : Exception}

    \clsdsp{A generic encoding exception that all specialized encoding exceptions derive from.}
\end{class}

\begin{class}{DecodingException}
    \clsdcl{public class DecodingException : Exception}

    \clsdsp{A generic decoding exception that all specialized decoding exceptions derive from.}
\end{class}