\chapter{Introduction}
\label{ch:introduction}
This Software Design Document discusses the software architecture as well as all packages, down to the individual classes. In order to aid development, the purpose of each package and class are briefly discussed. Additionally, the exposed (public) attributes and functions of each class are defined as a means to provide clear requirements which have to be met by the implementation. To allow for a better understanding of the interactions between multiple components, the written explanations are supplemented by static as well as dynamic diagrams.

\section{Purpose}
The purpose of this document is to provide a comprehensive description of the software design in order to provide a software development team with an understanding of all individual components and requirements. The contained information is supposed to be sufficient to implement the software in a way which is satisfying both the specifications listed in the Functional Specification Document as well as the architectural guidelines specified in this Software Design Document.

\section{Scope}
MORR is a software designed to collect data on the medical online research processes conducted by doctors and cancer researchers. This data is intended to be leveraged by computer scientists in order to try and detect patterns in these research processes, which would ultimately allow for prediction mechanisms to be created, benefiting future research in this medical field.

\section{Overview}
This document will first introduce the reader to the overarching software architecture and the project layout to provide an overview. Afterwards, the packages and their respective responsibilities will be discussed. Consecutively, the individual classes and their members will be described. The last chapter of this document contains several dynamic diagrams illustrating the control- and data-flow within the application.