\documentclass[aspectratio=169]{beamer}

\usetheme{metropolis}
\usepackage{xcolor}
\usepackage{stringstrings}
\newlength\MAX  \setlength\MAX{0.5\textwidth}
\newcommand*\Chart[1]{\substring{#1}{3}{4}\%~\rlap{\textcolor{black!20}{\rule{\MAX}{1.5ex}}}\rule{#1\MAX}{1.5ex}}
\title{MORR: Product presentation}
\author{Irma Suppes, Karl Rubel, Ming5yi Li, Niklas Bülow, Sönke Jendral}
\date{26th of March, 2020}
\institute{KIT / Teco}
\begin{document}
  \maketitle
  
  \begin{frame}{MORR}
      Medical Online Research Recorder
  \end{frame}

  \section{What is the goal that we try to accomplish?}

  \begin{frame}{The goal we try to accomplish}
    Our goal is to develop an application which records multiple kinds of user interactions during online medical researches.\\
    The recorded data will support data scientists to perform target page prediction.
  \end{frame}

  \section{What are the problems that are derived from this goal? \\And how has our application solved these problems?}
  
   \subsection{Data recording}
   
   \begin{frame}{Problem 1}
       What kind of user interactions are most likely to help the target page prediction?\\
       We must be able to record these interactions.
   \end{frame}
   
   \begin{frame}{A basic scope of recording, the Solution to Problem 1}
    Our application records:
        \begin{itemize}
            \item  Desktop video
            \item Clipboard:  cut, copy, paste
            \item Keyboard:  key presses and modifiers
            \item  Mouse:  mouse clicks, movement and scroll wheel interactions
            \item Window management:  window focus, movement, resizing, state changes
            \item Web browser:  button click, tab open/close/switch, file download, element hover,navigation, text input, text selection
        \end{itemize}
   \end{frame}
   
   \subsection{Extendability}
   \begin{frame}{Problem 2}
       There are way more other user interactions with valuable information.\\
       How can we allow the possibility to record them?
   \end{frame}
   
   \begin{frame}{Extendability, the Solution to Problem 2}
   We encapsulate the logic to record a certain type of user interaction in a module.\\
   And we use the Managed Extensibility Framework (MEF) to export each of the modules to the rest of the application.\\
   In this way, any other developer can extend the scope of the recorded user interactions by their own modules.
   \end{frame}
   
   \subsection{Configurability}
   \begin{frame}{Problem 3}
       Sometimes, not all user interactions produce values to target page prediction.\\ What if for example only the attention to mouse and keyboard interactions is needed?
   \end{frame}
   
   \begin{frame}{Configurability, the Solution to Problem 3}
   We let the entire application to be configurated by a .json file. ??? detail needed???
   \end{frame}
   
   \subsection{Useability and User-interface}
  \begin{frame}{Problem 4}
       Our target, the doctors who conduct online medical researches, are expected to have no knowledge on any technical details in any part of our project.
   \end{frame}
   
   \begin{frame}{???, the Solution to Problem 4}
   \begin{itemize}
          \item easy to install: short and clear user Manual?????
          \item easy to learn: Simple User-interface and ????
          \item easy to use: user freindly instruction and  error dialog?????????
      \end{itemize}
   \end{frame}

   \input{stats}

\end{document}