\chapter{Application Data}
\label{ch:data}

The application's main purpose is all about collecting data. This data is supposed to help to find patterns in research activity using a personal computer. Therefore there is a great range of distinctive data sets that are interesting to collect.

\section{Sessions}
\begin{itemize}

\item[/D100/] All sessions are stored locally in a document-based database and may be uploaded on a remote database storage.

\item[/D110/] Each general session needs to include the following data:
	\begin{itemize}
	\item Unique session id
	\item Date of start and stop
	\item Duration
	\item Video-output stream
	\end{itemize}
\end{itemize}

\section{Events}

Each dataset in a session is described by an event, which has been recognized and issued by a module. Each event includes multiple properties, which define and describe the event.

\begin{itemize}
\item[/D200/] A event must always include the following data:
	\begin{itemize}
	\item Timestap of the occurrence of the data
	\item Identifier of the module the event came from
	\item Type which identifies the events general action, e.g. a "MouseClick"
	\end{itemize}
\end{itemize}

\subsection{Window Management Events}

A window-management event is issued by the window-management module.

\begin{itemize}
\item[/D210/] A general Window-Management event must include the follwing data:
	\begin{itemize}
	\item The name of the interacted window
	\item The process associated with the window
	\end{itemize}

\item[/D220/] A Window-Focus event should only include the general data.

\item[/D230/] A Window-Movement event should include following additional data:
	\begin{itemize}
	\item Old and new location
	\end{itemize}
	
\item[/D240/] A Window-Resizing event should include following additional data:
	\begin{itemize}
	\item Old and new window size
	\end{itemize}
	
\item[/D250/] A Window-Maximizing/Minimizing event should include following additional data:
	\begin{itemize}
	\item The new state of the window, e.g. "Maximized".
	\end{itemize}
\end{itemize}

\subsection{Mouse Interaction Events}

A mouse-interaction event is issued by the mouse module.

\begin{itemize}
\item[/D260/] A general Mouse-Interaction event must include the following data:
	\begin{itemize}
	\item 
	\end{itemize}
\end{itemize}

\subsection{Keyboard Interaction Events}

A keyboard-interaction event is issued by the keyboard module.

\begin{itemize}
\item[/D270/] A general Keyboard-Interaction event must include the following data:
	\begin{itemize}
	\item Tapped keys, can be a single or multiple keys
	\end{itemize}
\end{itemize}

\subsection{Clipboard Events}

A clipboard event is issued by the clipboard module.

\begin{itemize}
\item[/D270/] A Clipboard-Interaction event must include the following data:
	\begin{itemize}
	\item The value of the contained text
	\item Interaction type: "Copy" or "Paste"
	\end{itemize}
\end{itemize}

\subsection{Browser Events}

A browser event is issued by the browser module.

\begin{itemize}
\item[/D270/] A general Browser event must include the following data:
	\begin{itemize}
	\item The url of the interacted website
	\end{itemize}
\end{itemize}